Viscous Transport in Eroding Porous Media

### 2019-07-25 docs/transport/erosion_transport.tex
adding a few references

>>>>

\item The classic work of Carman~\cite{car1937} reviews early work on
granular flow.

\item Thermal boundary layer flow in anisotropic porous media is
investigated by Nilsen and Storesletten~\cite{nil-sto1990} and Rees and
Storesletten~\cite{ree-sto1995}.

\item \cite{won-kop-tom1984} investigates relationships between the
porosity of a rock to its permeability, surface area, and the electrical
conductivity of salt water within the rock.  They show that the pore
size distribution influences both the conductivity and permeability.

\item In~\cite{rot1988}, Rothman applies a cellular automaton method to
simulate flow in porous media.  The method is probabilistic and agrees
well with analytic solutions.  However, the resulting flow is not
smooth, so quantities such as the shear stress is challenging to stably
compute.

\item In~\cite{leb-den-car2008}, a statistical model is used to describe
transport in a high heterogeneous porous media.
